# Types

## Integers

There are different integers primitives that are built-in:

```{r int_types, echo = FALSE}
data_frame(
  Type = c(paste("Int", 2 ^ seq(3,6), sep = ""), paste("UInt", 2 ^ seq(3,6), sep = "")),
  `Smallest Value` = c(paste("-2^", (2^seq(3, 6) - 1), sep = "" ), rep(0,4)),
  `Largest Value` = c(paste("2^", (2^seq(3, 6) - 1),"\t-1",sep = "" ), paste("2^", (2^seq(3, 6)),"\t-1",sep = "" ))
) %>% 
  kable
```

Since Julia is **not** an **strongly typed** language it has to have a default integer type and it depends on the architecture of the CPU. Modern computers run on a 64-bit architecture and the default would be *Int64*.

Signed integers would be written as normal integers, i.e $1$ , $123456$. Unsigned integers are input and output using `0x` prefix and hexadecimal and the size is determined by the number of hex digits used:

```{julia unsigned_int}
typeof(0x1)
typeof(0x123)
typeof(0x1234567)
typeof(0x123456789abcdef)
```

If you forget the minimum or maximum value of each *integer type* you can use `typemin()` and `typemax()` functions:

```{julia type_min_max}
typemin(Int64)
typemax(Int64)
```

### Overflow behavior

The arithmetic of Julia *integers* is of the form of **modular arithmetic**, i.e **wrap around** behavior. This functionality is reflects the arithmetic of integers on computers. This is an important thing to consider when you make operations where overflow might happen. 

```{julia wrap_around_arithmetic}
typemax(Int64) + 1
```

## Floating-Point Numbers

There are different float primitives that are built-in:

```{r float_types, echo = FALSE}
data_frame(
  Type = paste("Float", 2 ^ seq(4,6), sep = ""),
  Precision = c("half", "single", "double"),
  Bits = (2^seq(4, 6))
) %>% 
  kable
```

To let *Julia* know you require floating point numbers the you need to add **.** to the number or use scientific notation:

```{julia, float_declaration}
1.
1.0
0.1
.1
1e0
```

If you are working on a *64-bit* machine this sort of numbers will be of the type `Float64`, if you want to use `Float32` you will need to use scientific notation and instead of *e* use *f*:

```{julia float32_declaration}
1f0
```

### Special values

In all types of float there are special values:

- **Positive Infinity** `Inf`: value greater than the largest value of the floating point.
- **Negative Infinity** `-Inf`: value less than the minimum value of the floating point.
- **Not a number** `NaN`: some value not equal to any floating point value.

## Operators

```{r arithmetic_operators, echo = FALSE}
data_frame(
  Expression = c("+", "-", "* ", "/", "\\", "^", "%"),
  Operator = c("Plus", "Minus", "Times", "Divide", "Inverse Divide", "Power", "Remainder"),
  Examples = c("x + y", "x - y", "x \\* y", "x / y", "y  x = x / y", "x ^ y", "x % y")
) %>% 
  kable
```


## Complex and Rational Numbers

## Strings
